Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex

>>>>

=======
\documentclass[a4paper,twoside]{article}

\subsection{OpenStack}
\label{sec:openstack}

One of the most prominent open-source cloud computing platform for both private 
and public clouds is OpenStack. The OpenStack project was announced in 2010 by 
Rackspace and NASA, and currently developed and distributed by the OpenStack
Foundation with the support of more than 150 relevant companies. OpenStack is a 
cloud operating system that provides Infrastructure as a Service (IaaS) able to 
control large pools of compute, storage, and networking resources throughout a 
datacenter, all managed through a dashboard or an API that gives administrators 
control while empowering their users to provision resources through a web interface
or a command-line. It supports most available hypervisors and handles provisioning 
and life-cycle management of VMs.

The first of them was {\it Montecarlo Multigpu} from NVIDIA SDK, launched with the default configuration ``scaling=weak'' which adjust the size of the problem depending on the number of accelerators.
The Figure~\ref{fig:mont-opt} depicts the options per second calculated by the application running on the scenarios of~\ref{fig:aws} and on the instances with local GPUs. 
We have removed the results of the Scenario~\ref{subfig:aws2} for clarity ought to they are exactly the same that the obtained from Scenario~\ref{subfig:aws3} up to 8 GPUs. 
In other words, we could state that the results until the 8th GPU would correspond to the Scenario~\ref{subfig:aws2} and thereafter to the Scenario~\ref{subfig:aws3}.
Hence, in this particular case, rCUDA (using remote GPUs) is performing better than CUDA (with its local GPUs) due to rCUDA loads the libraries when its daemon starts.
However, even with rCUDA we can see differences in the results between booth scenarios. We determined that the Scenario~\ref{subfig:aws1} could increase the throughput because
unlike the other setups the GPUs are not sharing the PCI bus with other devices, as it happens in the 4-GPU instances.

% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=\linewidth]{images/aws-mont2.png}
%   \caption{Montecarlo execution time}
%   \label{fig:mont-exe}
% \end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont1.png}
  \caption{Montecarlo options per second}
  \label{fig:mont-opt}
\end{figure}

Flexibility and economical expenses
